\LARGE \bf Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]

### 2014-10-01 paper.tex
mergy

\begin{abstract}
Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.  %%PA: not sure what "Bayesian shape represenation" means -- isn't it just a distribution over shapes that it represents, which happens to allow for performing Bayesian inference?  language not very precise I guess...
Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a %%PA: a -> an
 evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.%%PA: grouping of words should try to make things easier to read/follow along; does 2D only apply to the O(n^6) or to the entire sentence?  aside from sentence structuring, it's hard to understand this previous sentence, what is the n^9 about? what is a grid step?  does it mean number of discretization levels for dimension?
%%PA: also, why ".." rather than "." to end the sentence?
We propose an alternative approximation%%PA: grouping of words is off; it's not an alternative approximation, it 's an alternative to sampling from shape distributions ..
 to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. 
%%PA: how about including some intuition about what the alternative is / what main idea it is leveraging?
We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps.  %%PA: --> cool!!
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%PA: this citation type-setting is a bit funny to me, I am much more used to [12, 8, 10] or [12], [8], [10] rather than the current paper's typesetting as [12] [8] [10].  If you have seen it in a reputable place and it's the style you guys prefer then I am fine with it, of course
%%ZM: fixed

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity%%PA: --> spelling
 in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}. %%PA: why two dots? %%PA: and same paper is cited twice... %%ZM: fixed

While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous real-valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface. This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}. To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field. Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they also allow for a differentiable function as a shape representation, 
%%PA: continuous and differentiable (which I believe would be a redundant statement as differentiable implies continuous), or continuously differentiable? %%ZM: fixed
which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
\caption{Left: HD image of a common measuring cup from in a household environment. Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. 
%%PA: that's neat!  let's have you include some of that in the abstract!
%%PA: also n^3 independent as to whether it's a 2-D or 3-D problem, or is n^3 specific to a particular dimensionality?
We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory. In light of this our contributions are the following:

\begin{enumerate}
	\item Derivation of distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.%%PA: grammar off
	\item Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.%%PA: -> computational %%ZM: fixed
	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
\end{enumerate}

@@

 Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}, \cite{goldberg1990stochastic}, \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}, \cite{felip2009robust}, \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.  Christopoulo et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.

 The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual. Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}, \cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}. Some exciting work done with GPIS representation are the following: Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}. Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}. Mahler et al. used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}. %%PA: locally optimal anti-podal grasps?

  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace. We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.

Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}. While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}, \cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.  Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}. Prior work by Kehoe et al. \cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed. To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}. Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
\caption{Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle. Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.  }
\vspace*{-10pt}
\label{fig:GPIS_TSDF}
\end{figure}
%\section{Related Work}

For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}. %%PA: motivation seems a little weak; did you compare performance with other kernels? (must be other differentiable ones?) could something be added about why differentiability is important to our approach?

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.

@@

Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$. To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. See Fig. \ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like. For computational reasons we approximate the integral via Monte-Carlo Integration. We use importance sampling to draw from the distribution induced by GPIS and calculate the following

@@

\begin{align*}
E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S) %%PA: 1/N missing?
\end{align*}

@@

Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.  Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}. %%PA: that last use of $n$ has a different meaning, that's confusing, use a different symbol than n, or just say in words it's cubic in the number of grid points
Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. To sample contact points, one can simply draw samples from Eq. \ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies conditions \ref{list:contact_cond}.

We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

@@

Where $\eta$ is a proportionality constant. The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.  We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig.
\ref{fig:GraspDist}.

@@

In practice Eq. \ref{eq:contact_theory} is not efficient to compute because it requires computation of the cumulative distribution function of a large multivariate Gaussian, so instead we sample from Eq. \ref{eq:line_of_act_dist} and find the first positive to negative zero-crossing of the sample along the line.

>>>>

\begin{abstract}
Gaussian Process Implicit Surface (GPIS) have emerged recently as a new Bayesian shape representation.  Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. The standard approach of drawing samples from a GPIS in 2D by means of a evaluation on a uniform grid has a complexity of $O(n^6)$(2D) and $O(n^9)$ in the number of grid steps $n$.. We propose an alternative approximation to sampling from shape distributions and demonstrate how that reduce complexity from $O(n^6)$ in 2D and $O(n^9)$ in 3D to $O(n^3)$ for evaluation of a single grasp. We furthermore introduce the idea of adaptive sampling in this context by formulating it as a multi-arm bandit problem for speeding up the selection of the highest quality grasp in a set of proposed grasps. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainity in the shape of the object \cite{kehoe2012estimating} \cite{kehoe2012estimating} \cite{christopoulos2007handling} \cite{zheng2005}..

While past work has encoded uncertainty in a polygonal mesh representation \cite{kehoe2012estimating}, an alternative is to work with the signed distance fields (SDFs), a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface. This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}\cite{curless1996volumetric}. To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field. Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}\cite{jeffs}\cite{hollinger2013}.

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=4cm]{figures/Slide02.jpg}
\caption{\footnotesize
Left: HD image of a common measuring cup from in a household environment. Right: Image taken from PR2's Primesense Carmine sensor, large parts of the measuring cup are not detected by the depth sensor and are not visible in the RGB image.}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

Given a method to represent shape uncertainty, a common technique to evaluate grasp quality is to sample from the distribution on shape and perform Monte-Carlo integration on a given grasp metric \cite{kehoe2012estimating}\cite{kehoe2012toward}\cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory. In light of this our contributions are the following:

\begin{enumerate}
	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
	\item  Demonstrating both theoretically and empirically how those distributions reduce the computationally complexity of sampling.
	\item Applying adaptive sampling techniques to efficiently find high quality grasps in a given set of proposed grasps. 
\end{enumerate}

@@

 Past work on grasping under uncertainty has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this approach was limited to polygonal shapes.  Christopoulo et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainty, however it is has not been shown how a spline based method could incorporate non-visual sensing information for representing shape uncertainty.

 The choice of using Gaussian Process Implicit Surfaces to represent uncertainty, is based on the fact it provides a formal way to include various sources of noise from observations such as tactile, laser and visual. Futhermore, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric}\cite{newcombe2011kinectfusion}\cite{hornung2013octomap}. Some exciting work done with GPIS representation are the following: Hollinger et al. used GPIS to perform active sensing on the hulls in underwater boats \cite{hollinger2013}. Dragiev et al. showed how GPIS can represent shapes for grasps and used  as a grasp controller on the continuous signed distance function \cite{dragiev2011}. Mahler et al. used GPIS representation to find locally optimal grasps by framing grasp planning as an optimization problem \cite{jeff}.

  For grasp quality evaluation with shape uncertainty a common method involves sampling from the distribution on shape \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}. With GPIS this requires computationally intensive sampling from a signed distance field that is the dimension of the workspace. We propose an alternative distribution to sample from, based on the idea that we only need to consider the approach trajectory of the gripper.

Monte-Carlo integration involves drawing random samples from a distribution to approximate an integral \cite{caflisch1998monte}. While previous work has looked at quality evaluation of a single grasp with uncertainty \cite{christopoulos2007handling}\cite{zheng2005}, few have compared many different grasps with uncertainty and efficiently chosen the best one.  Adaptive Sampling is the idea of allocating samples based on previous observations or rewards, which can be described as a multi-arm bandit problem \cite{barto1998reinforcement}. Prior work by Kehoe et al. \cite{kehoe2012toward} used an adaptive sampling approach that removed low quality grasps based on values received, but this method had no statistical guarantees and could lead to high quality grasps being removed. To achieve guarantees, we frame the problem as a "budgeted multi-arm bandit" problem, where exploration and exploitation are decoupled and the agent has to allocate resources to explore for a finite time then decide which arm to exploit  \cite{madani2004budgeted}. Drawing from the literature on Monte-Carlo sampling we estimate the confidence bounds of grasps and prune only those that are statistically distinguishable \cite{caflisch1998monte}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle. Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.  }
\vspace*{-10pt}
\label{fig:GPIS_TSDF}
\end{figure}
%\section{Related Work}

For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull doesn't enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = \lbrace \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} \rbrace$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}\cite{li1988task}.

@@

Where $Q(g|S,\Gamma)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$. To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating} \cite{kehoe2012toward} \cite{christopoulos2007handling}. See Fig. \ref{fig:shape_samples} for an example of what samples drawn from $p(S)$ induced by GPIS look like. For computational reasons we approximate the integral via Monte-Carlo Integration. We use importance sampling to draw from the distribution induced by GPIS and calculate the following

@@

\begin{align*}
E(Q(\Gamma)) \approx \sum_{i=1}^N Q(g|S_i,\Gamma) , S_i \in p(S)
\end{align*}

@@

Thus if the workspace is an $n \times n$ grid, the joint distribution is an  $n^2$ multi-variate Gaussian, due to $sd:\mathbb{R}^2 \rightarrow \mathbb{R}$.  Sampling from a Gaussian involves inverting the covariance matrix and inversion is in the naive way $O(n^3)$ \cite{petersen2008matrix}. Thus the complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D.

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. To sample contact points, one can simply draw samples from Eq. \ref{fig:line_of_action} and iterate from $a$ to $b$ until they reach a point that satisfies  Eq. \ref{eq:density_cond} and Eq. \ref{eq:cdf_cond}.

We also derive what the actual distribution $p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ in case the reader wanted the actual distribution and not samples. Using the conditions described above for a contact point( Eq. \ref{eq:density_cond} and Eq. \ref{eq:cdf_cond}).  We write the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

@@

Where $\eta$ is a proportionality constant. The first product in the equation can be computed easily using the marginalization of a multivariate Gaussian distribution and the second term can be solved by first conditioning on the joint $p(sd(\gamma(t))|sd(\gamma(t)) = 0)$ and then computing the cumulative distribution function  \cite{petersen2008matrix}.  We show the theoretical distribution on $\textbf{c}_i$ calculated for a given GPIS and line of action in Fig \ref{fig:GraspDist}. As mentioned earlier, Eq. \ref{eq:contact_theory} is not efficeint to compute due to cumulative distribution function of a large multi-variate Gaussian, however GPIS's ability to give a distribution on contact points is still interesting.

@@
